---
title: "Assignment_2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(ggplot2)
library(Hmisc)
library(ggthemes)
```



```{r}
apps <- read.csv("googleplaystore.csv", stringsAsFactors = FALSE)

f <- function(x){
  length(unique(x))
}
sapply(apps, f)
unique(apps$Category)

as.data.frame(table(apps$Category)) %>% arrange(Freq)
```

Selected topics:

Medical, game, productivity, business, health, social
Are you getting bang for your buck
Targets: installs, ratings (satisfaction), reviews,
independent variable: price


Questions:

Does ratings/ satisfaction vary with price (regression)?
  Is this mediated by number of reviews?
Does number of installs vary with price (regression)?
  Is this also mediated by number of reviews

```{r, echo=FALSE}

select_apps <- apps %>% filter(Category %in% c("GAME", "MEDICAL", "BUSINESS", "PRODUCTIVITY", "LIFESTYLE", "SOCIAL"))
sapply(select_apps, class)
select_apps$Category <- as.factor(select_apps$Category)
select_apps$Reviews <- as.numeric(select_apps$Reviews)
select_apps$Installs <- factor(select_apps$Installs, levels = c("0+", "1+", "5+", "10+", "50+", "100+", "500+", "1,000+", "5,000+", "10,000+", "50,000+", "100,000+", "500,000+", "1,000,000+", "5,000,000+", "10,000,000+", "50,000,000+", "100,000,000+", "500,000,000+", "1,000,000,000+"), ordered = TRUE)
levels(select_apps$Installs)

select_apps$Price <- gsub('\\$', "", select_apps$Price)
select_apps$Price <- as.numeric(select_apps$Price)

```



```{r}
colSums(is.na(select_apps))

```


```{r}
library(itertools)
variables <- colnames(select_apps)
unlist(as.list(enumerate(variables)))
screen <- lapply(variables, function(i) ggplot(data = select_apps, aes_string(x=i)) + geom_histogram())

#rating
screen[[3]]

#reviews
screen[[4]]

#price
screen[[8]]
```
```{r}
#filter outliers for reviews
reviews <- ggplot(select_apps, aes(x = factor(1), y = Reviews))
reviews <- reviews + geom_boxplot(width = 0.25)
reviews

box <- ggplot_build(reviews)
box$data[[1]][1:5]

apps_clean <- filter(select_apps, Reviews <2225104)
reviews2 <- ggplot(apps_clean, aes(x = factor(1), y = Reviews))
reviews2 <- reviews2 + geom_boxplot(width = 0.25)
reviews2
qplot(Reviews, data = apps_clean, geom = "histogram" )
#plot is positively skewed

```

```{r}
price <- ggplot(apps_clean, aes(x = factor(1), y = Price))
price <- price + geom_boxplot(width = 0.25)
price

box2 <-ggplot_build(price)
box2
box2$data[[1]][1:5]


library(outliers)
z.scores <- apps_clean$Price %>% scores(type = "z")
z.scores %>% summary()

apps_clean <- filter(select_apps, Price <22)

price2 <- ggplot(apps_clean, aes(x = factor(1), y = Price))
price2 <- price2 + geom_boxplot(width = 0.25)
price2
qplot(Price, data = apps_clean, geom = "histogram" )

```

```{r}
rate_price <-ggplot(data = apps_clean, aes(x = Price, y = Rating))
rate_price + geom_point(position = "jitter")
```

```{r}
# levels(apps_clean$Installs) <- list(`0-100`= c("0+", "1+", "5+", "10+", "50+"), `101 - 1,000` = c("100+", "500+") , `1,001 - 10,000` = c("1,000+", "5,000+"), `10,001 - 100,000`= c("10,000+", "50,000+"), `100,001 - 1,000,000` = c("100,000+", "500,000+"), `1,000,001 - 10,000,000` = c("1,000,000+", "5,000,000+"), `10,000,001 - 100,000,000`= c("10,000,000", "50,000,000+"), `> 100,000,000` = c("100,000,000+", "500,000,000+", "1,000,000,000+"))  

levels(apps_clean$Installs) <- list(`10^2`= c("0+", "1+", "5+", "10+", "50+"), `10^3` = c("100+", "500+") , `10^4` = c("1,000+", "5,000+"), `10^5`= c("10,000+", "50,000+"), `10^6` = c("100,000+", "500,000+"), `> 10^7` = c("1,000,000+", "5,000,000+", "10,000,000", "50,000,000+", "100,000,000+", "500,000,000+", "1,000,000,000+")) 


levels(apps_clean$Installs)
```

```{r}
installs_price <- ggplot(data = apps_clean, aes(x = Price, y = Installs, colour = Rating))
installs_price + geom_point(position = "jitter") + scale_colour_gradient2_tableau(palette = "Red-Blue Diverging") + scale_alpha("Rating")

```


```{r}
reviews_installs <- ggplot(data = apps_clean, aes(x = Reviews, y = Installs, colour = Rating))
reviews_installs + geom_point(position = "jitter") + xlim(0, 50) + scale_colour_gradient2_tableau(palette = "Red-Blue Diverging") + scale_alpha("Rating")

```

```{r}
#add column with mean rating per group
apps_clean_gp <- apps_clean %>% group_by(Installs) %>% summarise (Mean_Rating = mean(Rating, na.rm = TRUE))
apps_clean2 <- merge(apps_clean, apps_clean_gp)


installs_price2 <- ggplot(data = apps_clean2, aes(x = Installs, y = Price, colour = Rating))
v_install_price2 <- installs_price2 + geom_violin(width = 0.75, aes(fill = Mean_Rating)) + ylim(0.99,10)
v_install_price2 + scale_colour_gradient2_tableau(palette = "Red-Blue Diverging") + scale_alpha("Rating")

#v_install_price + geom_point(position = "jitter") + scale_colour_gradient2_tableau(palette = "Red-Blue Diverging") + scale_alpha("Rating")

```



```{r}
v_install_price2 + facet_wrap(~ Category)
```







```{r}
diamonds <- diamonds
diamonds_group <- diamonds %>% group_by(cut) %>% summarise(Mean_Price = mean(price))
diamonds_group

diamonds2 <- diamonds
diamonds2 <- merge(diamonds2, diamonds_group)

ggplot(diamonds2, aes(x=cut,y=carat)) + geom_boxplot(aes(fill=Mean_Price)) + scale_fill_gradient2(midpoint = mean(diamonds2$price))
```

